\documentclass[10pt]{amsart}
\usepackage[foot]{amsaddr}
\usepackage[numbers]{natbib}
\usepackage{listings}

% \usepackage[left=0.5in]{geometry}
\usepackage[left=1in,top=1in,right=1in,bottom=1in,head=.1in]{geometry}
\usepackage{graphicx}
% \usepackage{xcolor}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{constants}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{mathrsfs} 
\usepackage{bm}
\usepackage{bbm}
\usepackage{hyperref}
\usepackage{todonotes}

\hypersetup{
    colorlinks=true,
    citecolor=blue,
    linkcolor=red,
    filecolor=magenta,      
    urlcolor=RoyalBlue
}
\usepackage{cleveref}
\usepackage[toc,page]{appendix}
\usepackage{caption}
\usepackage{subcaption}

\date{\today}
\title{Takuya Koriyama}
\begin{document}
\maketitle
\begin{center}
  Personal website \url{https://takuyakoriyama.github.io/}.
Email: tkoriyam@uchicago.edu
\end{center}
\subsection*{Education}
\begin{itemize}
  \item 2024-present: PhD student in Econometrics and Statistics, the University of Chicago, Booth School of Business. Advisor: \href{https://tyliang.github.io}{Tengyuan Liang}. 
  \item 2022-2024 PhD student in Statistics, Rutgers University. Advisor: \href{https://statweb.rutgers.edu/PCB71/}{Pierre C. Bellec}. 
  \item 2018-2022: BE in Mathematical Engineering, the University of Tokyo. 
  % Advisors: Takeru Matsuda and Fumiyasu Komaki
\end{itemize}

\subsection*{Research Interests} (\href{https://scholar.google.com/citations?user=JOqLea0AAAAJ&hl=en&oi=ao}{Google Scholar})
\noindent
% My research interests span probability, optimization, and statistics, with a focus on (1) statistical and computational learning theory for generative models, (2) high-dimensional statistics in the mean-field regime, (3) the interplay between high-dimensional probability and convex geometry.
% I have broad interests in mathematical theory and algorithms. In recent years, my research has focused on:
\begin{itemize}
\item Mean-filed high-dimensional statistics
\item  Optimal transport and its application to generative model
\item  Training dynamics of modern machine learning models 
\item  Combinatorial stochastic processes
\end{itemize}


\subsection*{Preprint}
\begin{enumerate}
\item \href{https://arxiv.org/abs/2506.21527}{Asymptotic Inference for Exchangeable Gibbs Partition}\\
Takuya Koriyama\\
\textit{arXiv:2506.21527, 2025, submitted.}

\item \href{https://arxiv.org/abs/2404.02070}{Asymptotics of resampling without replacement in robust and logistic regression}\\
Pierre C. Bellec and Takuya Koriyama (alphabetical)\\
\textit{arXiv:2404.02070, 2024, major revision at \textbf{Bernoulli.}}

\item \href{https://arxiv.org/abs/2312.13254}{Existence of solutions to the nonlinear equations characterizing the precise error of M-estimators}\\
Pierre C. Bellec and Takuya Koriyama (alphabetical)\\
\textit{arXiv:2312.13254, 2023, submitted.}
\end{enumerate}

\subsection*{Publication}

\begin{enumerate}
  \item \href{https://arxiv.org/abs/2411.01629}{Denoising Diffusions with Optimal Transport: Localization, Curvature, and Multi-Scale Complexity}\\
  Tengyuan Liang, Kulunu Dharmakeerthi, and Takuya Koriyama \\
  \textit{Accepted to \textbf{Transactions on Machine Learning Research}.}

  \item \href{https://arxiv.org/abs/2409.15252}{Precise Asymptotics of Bagging Regularized M-estimators}\\
  Takuya Koriyama, Pratik Patil, Jin-Hong Du, Kai Tan, and Pierre C. Bellec \\
  \textit{Accepted to \textbf{Annals of Statistics}.}

  \item \href{https://doi.org/10.1017/apr.2025.10020}
  {Asymptotic mixed normality of maximum likelihood estimator for Ewens--Pitman partition}\\
  Takuya Koriyama, Takeru Matsuda and Fumiyasu Komaki\\
  \textit{\textbf{Advances in Applied Probability}, Published online 2025:1-21.}

  \item \href{https://arxiv.org/abs/2501.03163}{Phase transitions for the existence of unregularized M-estimators in single index models} \\
  Takuya Koriyama and Pierre C. Bellec\\
  \textit{\textbf{Proceedings of the 42nd International Conference on Machine
Learning} (ICML 2025)}.

  \item \href{https://jmlr.org/papers/v26/24-0060.html}{Error estimation and adaptive tuning for unregularized robust M-estimator}\\
  Pierre C. Bellec and Takuya Koriyama (alphabetical)\\
  \textit{\textbf{Journal of Machine Learning Research}  26 (16), 1-40, 2025.} 

  \item \href{https://doi.org/10.1093/jrsssb/qkae092}{Corrected generalized cross-validation for finite ensembles of penalized estimators}\\
  Pierre C. Bellec, Jin-Hong Du, Takuya Koriyama*, Pratik Patil* and Kai Tan (alphabetical)\\
  \textit{\textbf{Journal of the Royal Statistical Society: Series B}, 87(2), 289-318, 2025.} 

  \item  \href{https://www.tandfonline.com/doi/full/10.1080/07350015.2024.2326149?casa_token=_YOXJFqGXa0AAAAA%3AZCueJ9QbEp0N1Yvh8Bm0ieEefDcQECfZyzYWfPd2KTI_yxy9l7rt0cja6c5I4cyVJuAT7q2sfTzo}{Fully Data-driven Normalized and Exponentiated Kernel Density Estimator with Hyvärinen Score}\\
  Shunsuke Imai, Takuya Koriyama, Shouto Yonekura, Shonosuke Sugasawa and Yoshihiko Nishiyama\\
  \textit{\textbf{Journal of Business \& Economic Statistics} 43 (1), 110-121, 2025.
  }
\end{enumerate}

% \begin{enumerate}
% % \item \href{https://arxiv.org/abs/2501.03163}{Phase transition for unregularized M-estimation in single index model} \\
% % Pierre C. Bellec and Takuya Koriyama (alphabetical)\\
% % \textit{arXiv:2501.03163, 2025}.

% % \item \href{https://arxiv.org/abs/2411.01629}{Denoising Diffusions with Optimal Transport: Localization, Curvature, and Multi-Scale Complexity}\\
% % Tengyuan Liang, Kulunu Dharmakeerthi, and Takuya Koriyama \\
% % \textit{arXiv:2411.01629, 2024, under review at Annals of Statistics.}

% % \item \href{https://arxiv.org/abs/2409.15252}{Precise Asymptotics of Bagging Regularized M-estimators}\\
% % Takuya Koriyama, Pratik Patil, Jin-Hong Du, Kai Tan, and Pierre C. Bellec (alphabetical) \\
% % \textit{arXiv:2409.15252, 2024, under review at Annals of Statistics.}

% % \item \href{https://arxiv.org/abs/2404.02070}{Asymptotics of resampling without replacement in robust and logistic regression}\\
% % Pierre C. Bellec and Takuya Koriyama (alphabetical)\\
% % \textit{arXiv:2404.02070, 2024, under review at Bernoulli.}

% % \item \href{https://arxiv.org/abs/2312.13254}{Existence of solutions to the nonlinear equations characterizing the precise error of M-estimators}\\
% % Pierre C. Bellec and Takuya Koriyama (alphabetical)\\
% % \textit{arXiv:2312.13254, 2023, under review at Information and Inference: A Journal of the IMA.}

% % \item \href{https://arxiv.org/abs/2312.13257}{Error estimation and adaptive tuning for unregularized robust M-estimator}\\
% % Pierre C. Bellec and Takuya Koriyama (alphabetical)\\
% % \textit{arXiv:2312.13257, 2023. Major revision at Journal of Machine Learning Research.} 

% % \item \href{https://arxiv.org/abs/2310.01374}{Corrected generalized cross-validation for finite ensembles of penalized estimators}\\
% % Pierre C. Bellec, Jin-Hong Du, Takuya Koriyama, Pratik Patil and Kai Tan (alphabetical)\\
% % \textit{Journal of the Royal Statistical Society: Series B, 2024.} 

% % \item  \href{https://arxiv.org/abs/2212.00984}{Fully Data-driven Normalized and Exponentiated Kernel Density Estimator with Hyvärinen Score}\\
% % Shunsuke Imai, Takuya Koriyama, Shouto Yonekura, Shonosuke Sugasawa and Yoshihiko Nishiyama\\
% % \textit{Journal of Business \& Economic Statistics, 2024. }

% % \item \href{https://arxiv.org/abs/2207.01949}
% % {Asymptotic analysis of parameter estimation for the Ewens--Pitman partition}\\
% % Takuya Koriyama, Takeru Matsuda and Fumiyasu Komaki\\
% % \textit{arXiv:2207.01949, 2022. To appear in \textit{Advances in Applied Probability 58.1, 2026}.}
% \end{enumerate}

\subsection*{Award}
\begin{itemize}
  \item IMS Hannan Graduate Student Travel Award, 2025.
  \item Travel award, Yale FDS workshop honoring Andrew Barron, 2024. 
  \item Best Ph.D. Qualifying Exam Performance, Department of Statistics, Rutgers University, 2023.
  \item Student Travel Award, IMS International Conference on Statistics and Data Science, 2022.
  \item Best Presentation Award, 16th Japan Statistical Society Spring Meeting, 2022. 
  \item Japan Statistical Society Certificate Director's Award, 2022.
\end{itemize}

\subsection*{Talk}
\begin{itemize}
  \item Proceedings of the 42nd International Conference on Machine Learning (ICML), Vancouver, July 2025.
  \item  Workshop on Statistical Network Analysis and Beyond (SNAB), Tokyo, June 2025.
  \item  IMS International Conference on Statistics and Data Science, Nice, December 2024. 
  \item  Workshop Honoring Andrew Barron: Forty Years at the Interplay of Information Theory, Probability and Statistical Learning, Yale University, April 2024. 
  \item IMS Asia Pacific Rim Meeting, Melbourne, January 2024. 
  \item Seminar talk, Graduate school of Economics, the University of Tokyo, February 2023. 
  \item IMS International Conference on Statistics and Data Science, Florence, December 2022.
  \item  Workshop on random partition of integers, the University of Tokyo, June 2022.
  \item Japan Statistical Society Meeting, Keio University, March 2022.
\end{itemize}

\subsection*{Teaching} (PhD level courses)
\begin{itemize}
\item TA: Theory of Probability, fall 2023.
\item TA: Stochastic process, spring 2024.
\item Instructor: Probability and Stochastic Processes, summer 2024.
\end{itemize}



\end{document}